The ChEMBL database as Linked Open Data

### 2012-03-02 article.tex
add Bio2RDF paragraph and bibliography entries for three citations

@@

Peter: Bio2RDF

@@

Later, to satisfy the requirements for the Linked Open Drug Data \cite{}
network, the data was also hosted on Kasabi, a triple store hosting service
free for Open Data~\cite{}.

@@

>>>>

\bibliographystyle{plain}

@@

The Bio2RDF project provides both resolvable Linked Data URIs using a generic Linked Data server \cite{Ansell2011}, and access to SPARQL endpoints for a range of scientific databases \cite{Belleau2008}. A number of these databases are referenced in Chembl, including Chebi, Pubmed, and both the Uniprot protein and taxonomy databases. These links are vital to provide context for users who need to query across both Chembl and its related databases. The Linked Data server used by Bio2RDF has been configured for Chembl to provide URL based services for text and link searches.

@@

Later, to satisfy the requirements for the Linked Open Drug Data \cite{Samwald2011}
network, the data was also hosted on Kasabi, a triple store hosting service
free for Open Data~\cite{}.

@@

\bibliography{article}
